Empty Homes V1

### 2017-05-25 EmptyHomesV1.Rmd
Added functions
I added a load of functions to clean up and standardise the code.

Barnet <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2:8)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

@@

#Chelsea
# Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM)) 
# 
# Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(X.Ward) %>%
#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related., Empty..50..premium., Moorings , na.rm = TRUE),
#          LowUse = Empty + Second.Homes) %>% ungroup
# 
# Chelsea[is.na(Chelsea)] <-0
# rm(Chelwards)
# 
# Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
#   mutate(LowUsePerc = LowUse/WardHomes)
# 
# cor(Chel2$PrimePerc, Chel2$LowUsePerc)
# cor(Chel2$MeanPrice, Chel2$LowUsePerc)
# 
# Chel2 %>%
#   mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>% 
#   ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() + 
#   geom_smooth(method ="lm", se = FALSE) +
#   labs(title = "Relationship between % of Prime Sales and % Low Use", 
#        x = "% of properties sold in 2016 over £1M by electoral ward",
#        y = "% of properties either empty or second homes") +
#   theme(plot.title = element_text(hjust = 0.5))  +
#   coord_cartesian(xlim = c(15,78), expand = TRUE)
#  
# 
# 
# CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
#   filter(WD16NM!= "Kensal Green")

@@

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
  labs(title = "9 Boroughs: Ward Level % Empty") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

@@

AG2 %>% 
  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =EmptyPercRank), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()

@@

#single borough
CHELDAT %>%
  mutate(LowUsePerc = LowUse/WardHomes*100, 
         EmptyPerc = Empty/WardHomes,
         EmptyPercRank = percent_rank(Empty/WardHomes)) %>%
ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  labs(title = "Kensington and Chealsea: Ward Level % Low Use") +
  theme(plot.title = element_text(hjust = 0.5))+ 
  scale_fill_continuous(name = "Percentage")

@@

AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
  left_join(., select(Chelsea, LSOA_CODE, LowUse, Empty, Homes), by = c("lsoa11cd"="LSOA_CODE")) %>% 
  ungroup %>%
  filter(WD16NM!= "Kensal Green") %>%
  mutate(LowUsePerc = LowUse/Homes.y*100, 
         EmptyPerc = Empty/Homes.y*100,
         EmptyPercRank = percent_rank(Empty/Homes.y)) %>%
ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())+ 
  scale_fill_continuous(name = "Percentage")+
  ggtitle("Islington Exemptions")

@@

Cornwall %>% mutate(LowUsePerc = LowUsePerc*100) %>% 
  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
  ggplot(.)+ 
  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall: Ward level Empty and Second Homes %")+
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_fill_continuous(name = "Percentage")

@@

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
             x = 0.35 , y = 2.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)

 #"Cornwall: Relationship between LowUse\n Percentage and Mean Price in Ward"

@@

>>>>

Barnet <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
  setNames(c("ExemAG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
  filter(WD16NM!= "Kensal Green")ption.type", "LSOA_CODE", "X3", "X4")) %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
    setNames(make.names(trimws(names(.)))) %>% 
  mutate(LowUse = rowSums(.[,c(2:8)]), Empty = LowUse) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

@@

# Chelsea
# Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM))
# 
# Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(Ward) %>%
#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related, Empty..50..premium, Moorings , na.rm = TRUE),
#          LowUse = Empty + Second.Homes) %>% ungroup
# 
# Chelsea[is.na(Chelsea)] <-0
# rm(Chelwards)
# 
# Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
#   mutate(LowUsePerc = LowUse/WardHomes)
# 
# cor(Chel2$PrimePerc, Chel2$LowUsePerc)
# cor(Chel2$MeanPrice, Chel2$LowUsePerc)
# 
# Chel2 %>%
#   mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>%
#   ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() +
#   geom_smooth(method ="lm", se = FALSE) +
#   labs(title = "Relationship between % of Prime Sales and % Low Use",
#        x = "% of properties sold in 2016 over £1M by electoral ward",
#        y = "% of properties either empty or second homes") +
#   theme(plot.title = element_text(hjust = 0.5))  +
#   coord_cartesian(xlim = c(15,78), expand = TRUE)
# 
# 
# 
# CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
#   filter(WD16NM!= "Kensal Green")

@@

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptyPerc), 
colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
  labs(title = "Current London Data") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

SaveFig("London.png")

@@

AG2 %>% 
  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =EmptyPercRank), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
  labs(title = "Current London Data Coloured by Percent Rank") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

SaveFig("LondonPerc.png")

@@

#single borough

SingleB <- AG %>% filter(grepl("Kensington", LAD11NM))%>% 
  left_join(., select(Chelsea, Admin_ward_code, WardLowUse, WardLowUsePerc)) %>% 
  filter(WD16NM!= "Kensal Green") %>%
  mutate(WardLowUsePerc = WardLowUsePerc*100)

ggplot(SingleB) + 
  geom_polygon( aes(long, lat, group = group, fill = WardLowUsePerc), 
colour = alpha("black", 1/4), size = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(SingleB$WardLowUsePerc, na.rm = TRUE)) +
  labs(title = "Kensington and Chealsea: Ward Level % Low Use", fill = "Percentage") +
  theme(plot.title = element_text(hjust = 0.5)) +
    theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())

SaveFig("RBKCLowUse.png")

@@

Singlevis <- AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
  left_join(., select(Chelsea, LSOA_CODE, LowUse, Empty, Homes), by = c("lsoa11cd"="LSOA_CODE")) %>% 
  ungroup %>%
  filter(WD16NM!= "Kensal Green") %>%
  mutate(LowUsePerc = round(LowUse/Homes.y*100), 
         EmptyPerc = round(Empty/Homes.y*100),
         EmptyPercRank = percent_rank(Empty/Homes.y))

ggplot(Singlevis, aes(long, lat, group = group, fill = LowUsePerc))+ 
  geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(Singlevis$LowUsePerc))+
  theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())+ 
  ggtitle("Kensington and Chelsea Low use")

@@

C2 <- Cornwall %>% 
  mutate(LowUsePerc = LowUsePerc*100,
         WardLowUsePerc = WardLowUsePerc*100) %>% 
  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))

ggplot(C2, aes(long, lat, group = group, fill = WardLowUsePerc))+ 
  geom_polygon(colour = alpha("black", 1/4), size = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(C2$WardLowUsePerc, na.rm = TRUE))+
    theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())+ 
  labs(title = "Low Use Homes in the County of Cornwall", 
       fill="Percentage")     
SaveFig("Cornwall.png")

@@

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
             x = 0.35 , y = 2.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)#+
#   coord_cartesian(xlim=c(0,0.2), ylim= c(1e5, 3.5e+5))
SaveFig("CornCor.png")

@@

#Hull
```{r}

test <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  CleanData(.)

PlotMap(test,"Hull", variable = "WardLowUsePerc")
